### 2019-02-19 sections/intuition.tex
breakfast example

@@

A higher-order function which executes a given task twice.
\begin{TASK}
  let twice : Task $\tau$ -> Task $\tau$ = \t : Task $\tau$. t >>? \x . t
\end{TASK}
The task value of the first execution is ignored.
\qed

@@

This example demonstrates external communication and choice.
It is a vending machine that dispenses a small biscuit for one coin and a large biscuit for two coins.
\begin{TASK}
  let vend : Task String = enter Int >>? \n. if n == 1 then edit "small"
    else if n == 2 then edit "large"
    else fail
\end{TASK}
The editor $\Enter \Int$ asks the user to enter an amount of money.
This editor stands for a coin slot in a real machine that freely accepts and returns coins.
There is a continue button that is initially disabled, due to the fact that the left hand side of the step combinator has no value.
When the user has inserted exactly 1 or 2 coins, the continue button becomes enabled.
When the user presses the continue button, the machine dispenses either a large or a small biscuit, depending on the amount of money. \qed

>>>>

\begin{example}[Breakfast]

The following program shows the different collaboration operators in action.
The user has a choice whether they want tea or coffee.
They always get an egg.
The drink and the food are prepared in parallel.
When drink and food are prepared, the user can step to eating the result.

\begin{TASK}
  let makeBreakfast : Task Drink -> Task Food -> Task Unit =
    \makeDrink . \makeFood . makeDrink <&> makeFood >>? \<<d, f>>. eat d f
  let main : Task Unit =
    makeBreakfast (makeTea <?> makeCoffee) makeEgg
\end{TASK}

@@

A higher-order function which executes a given task twice.
\begin{TASK}
  let twice : Task $\tau$ -> Task $\tau$ = \t : Task $\tau$. t >>? \x . t
\end{TASK}
The task value of the first execution is ignored.

@@

This example demonstrates external communication and choice.
It is a vending machine that dispenses a small biscuit for one coin and a large biscuit for two coins.
\begin{TASK}
  let vend : Task String = enter Int >>? \n. if n == 1 then edit "small"
    else if n == 2 then edit "large"
    else fail
\end{TASK}
The editor $\Enter \Int$ asks the user to enter an amount of money.
This editor stands for a coin slot in a real machine that freely accepts and returns coins.
There is a continue button that is initially disabled, due to the fact that the left hand side of the step combinator has no value.
When the user has inserted exactly 1 or 2 coins, the continue button becomes enabled.
When the user presses the continue button, the machine dispenses either a large or a small biscuit, depending on the amount of money.
